Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654

### 2016-05-19 WRITEUP/ms.tex
done diff. lensing sec

Our model parameters in \Tab{lens}, describing
the mass distribution of the lensing galaxy, are consistent (within the uncertainties) 
with that of the SIE model presented by C06. We find a mass of 
$M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(7.47\,$\pm$\,0.02)\,$\times$\,10$^{11}$\,\Msun
within the Einstein radius.

\input{table_medianLens}

\subsubsection{Interpretation and Caveats} \label{sec:caveat}
The reconstructed source locations in \Fig{model} demonstrate
an intrinsic velocity gradient in the source plane, which is
indicative of a disk geometry. While solely based on the
lens model is insufficient to draw conclusive inference on its
true geometry. Additional support to the disk conjecture %conjecture of a disk morphology
can be found in the double-horned line profile (\Fig{CO21spec})
and the observed (image plane) velocity field (\Fig{CO21highO}). Furthermore,
C06 also find that the reconstructed source plane emission in optical-NIR
is best-reproduced using a $n$\,=\,1 Sersic profile.
Our interpretation therefore tends in favor of a disk morphology for RXJ1131.

@@

\subsubsection{Differential Lensing} \label{sec:differential}
Lens modeling of this source from previous studies find non-negligible
differential lensing effect across H-Band, V-band, and I-band. The
magnification factor ranges from 10.9 to 7.8, where the decrease is caused
by the more extended IR emission (hence \SF), well beyond the caustic (C06).

The highly asymmetric \bco line profile also suggests that differential lensing is non-negligible in the CO emission, where
flux density in the red wing is apparently much higher than in the blue wing, given its lensing configuration.
By modeling different kinematic components, we find that the magnification factor ranges from BLAH to BLAH. The various magnification factors are listed in \Tab{model}.
\input{table_magFactor}

>>>>

Our model parameters in \Tab{lens}, describing
the mass distribution of the lensing galaxy, are consistent (within the uncertainties)
with that of the SIE model presented by C06. We find a mass of
$M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(7.47\,$\pm$\,0.02)\,$\times$\,10$^{11}$\,\Msun
within the Einstein radius.
\input{table_medianLens}
\input{table_magFactor}

\subsubsection{Interpretation and Caveats} \label{sec:caveat} %DONE
The reconstructed source locations in \Fig{model} demonstrate
an intrinsic velocity gradient in the source plane, which is
indicative of a disk geometry. While solely based on the
lens model is insufficient to draw conclusive inference on its
true geometry. Additional support to the disk conjecture %conjecture of a disk morphology
can be found in the double-horned line profile (\Fig{CO21spec})
and the observed (image plane) velocity field (\Fig{CO21highO}). Furthermore,
C06 also find that the reconstructed source plane emission in optical-NIR
is best-reproduced using a $n$\,=\,1 Sersic profile.
Our interpretation therefore tends in favor of a disk morphology for RXJ1131.

@@

\subsubsection{Differential Lensing} \label{sec:differential} %DONE
Previous lens models of RXJ1131 find conspicuous
differential lensing effect across H-Band, V-band, and I-band (C06), where the
magnification factor ranges from 10.9 to 7.8. C06 attribute
the decrease toward the IR regime is caused by the more extended
IR emission, arising from \SF.
The highly asymmetric \bco line profile suggests that
differential lensing is non-negligible for the CO emission, where its red wing
is apparently much brighter than the blue wing, which is consistent
with the source positions relative to the caustics in \Fig{model}.
The red wing emission mainly originates near/at the cusp
in the caustic, whereas the blue wing emission is located beyond the caustics.
The magnification factor for CO thus ranges from 8.7 to 3.1 (\Tab{model}).
